\chapter{Abstract}
During the analysis of the existing application \emph{CCMail}, many mistakes have been discovered, which lead to the fact that \emph{CCMail} is not capable of meeting the new requirements. The software design and the database schema were neglected for a long time and didn't adapt to new standards, which leads to the fact that a refactoring is equal to an re-implementation. Nevertheless some features of \emph{CCMail} were adopted to \emph{CleverMail}. Especially, the e-mail sending process was adopted, except for the newly introduced features. The concept of \emph{CleveeMail} introduced new possibilities which are feasible now by using the JEE7 platform. The management of the template parameters will be a great challenge, because they are used in many aspects of the newly introduced \emph{CleverMail} application. Especially the consistency of these parameters needs to be ensured, because changes made on the template parameter specification have a far-reaching impact on the application.
\newline
\newline
Another challenge will be the integration into the other application components of the \emph{clevercure} system, because they are implemented in different Java versions and run on different runtime environments, were the supported and available technologies and frameworks differ. The concept of \emph{CleverMail} represents a good basis. An implemented prototype could be used to check the introduced concepts for usability. Last but not least it should be mentioned that it wasn't expected to find so much of \emph{CCMail} in \emph{CleverMail}. This will facilitate the move from \emph{CCMail} to \emph{CleverMail} and is considered to be a positive side effect. Some of the main differences between \emph{CCMail} and \emph{CleverMail} are:
\begin{itemize}
	\item The database is no longer the interface between \emph{CCMail} and the other applications such as \emph{CleverWeb},
	\item The integration into other software components is now possible and
	\item The e-mail templates are no longer static and can be defined and modified dynamically.
\end{itemize}
\ \newline
Especially the possibility to integrate \emph{CCMail} into other software components needs to be emphasized, since \emph{CCMail} didn't provided this feature at all, but is now a main part of \emph{CleverMail}. This will ensure that the implementations will be encapsulated within \emph{CleverMail} and can be used by other software components.